Technique for \earlywarning\ detection of compact binary coalescence and its implication for multimessenger astronomy

### 2011-06-01 results.tex
removed old text
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@814 ccdd05d5-56c1-461a-bf98-85f6876523b4

In this section we test our implementation of the \lloid\ method using the
pipeline described in the previous section.  We answer the following questions
\begin{itemize}
\item What is the measured loss of SNR due to the approximations used in the \lloid\ algorithm in a realistic analysis pipeline?
\item What is the measured latency of the implementation described in section 
\ref{sec:implementation}?
\item What is the measured computational cost of the implementation described in section
\ref{sec:implementation}?
\end{itemize}

@@

\FIXME{
I would like to see this section changed to emphasize the low-latency time
domain filtering 1. Use a live simulated white noise source (this ignores the
latency of whitening, but that goes beyond the scope of this paper, and we
mention this and perhaps suggest some exporation 2. Use TD filtering of N
templates 3. Present the performance and latency and provide estimates for
number of cores required for realtime ALIGO search based on current
infrastructure 4. Compute the impulse responses of the templates and histogram
the SNR loss for the SVD and time/slice/resampling 5. Put  a tee after some of
the low frequency stages and perhaps test the possibility of predictive
filtering (also with latency measurments) This will remove the complications of
running a full pipeline.  We need to sort things out before we do that, and
this paper should not be delayed any further.  The above tests will make the
point we need to make
}

\subsection{Detector noise characteristics}

We tested the new detection method with mock Advanced \textsc{ligo} data having a power spectrum prescribed by the ``zero detuning, high power'' noise model in \cite{Shoemaker:2009p9770}.

>>>>

In this section we test our implementation of the \lloid\ method using the
pipeline described in the previous section.  We answer the following questions
%
I) What is the measured loss of SNR due to the approximations used in the
\lloid\ algorithm in a realistic analysis pipeline?
%
II) What is the measured latency of the implementation described in section
\ref{sec:implementation}?
%
III) What is the measured computational cost of the implementation described in
section \ref{sec:implementation}?

@@

%\FIXME{
%I would like to see this section changed to emphasize the low-latency time
%domain filtering 1. Use a live simulated white noise source (this ignores the
%latency of whitening, but that goes beyond the scope of this paper, and we
%mention this and perhaps suggest some exporation 2. Use TD filtering of N
%templates 3. Present the performance and latency and provide estimates for
%number of cores required for realtime ALIGO search based on current
%infrastructure 4. Compute the impulse responses of the templates and histogram
%the SNR loss for the SVD and time/slice/resampling 5. Put  a tee after some of
%the low frequency stages and perhaps test the possibility of predictive
%filtering (also with latency measurments) This will remove the complications of
%running a full pipeline.  We need to sort things out before we do that, and
%this paper should not be delayed any further.  The above tests will make the
%point we need to make
%}

%\subsection{Detector noise characteristics}

%We tested the new detection method with mock Advanced \textsc{ligo} data having a power spectrum prescribed by the ``zero detuning, high power'' noise model in \cite{Shoemaker:2009p9770}.
